Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-02 GWLDCII.tex
updates from Monday's discussion

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size. \hlfix{By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,}{fix this citation} i.e.
\bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas

@@

\hlfix{Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.}{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
\bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
This holds if all poles of the integrands cancel. As a step towards this, in this section we prove some results about the structure of the denominator $R(W)$ of the integrand, as defined in Definition~\ref{def R(W)}.

>>>>

For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size. By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,\sanote{fix this citation} i.e.
\bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas

@@

Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.\sanote{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
\bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
This holds if all poles of the integrands cancel. As a step towards this, in this section we prove some results about the structure of the denominator $R(W)$ of the integrand, as defined in Definition~\ref{def R(W)}.
